---
title: "Homework 1 - MATH 318"
author: Bao Dang
output: github_document
---

**1. Download the data set hw1.csv.**

```{r}
library(readxl) # part of tidyverse
```

```{r}
hw1.csv = read.csv("C:\\Users\\I566801\\OneDrive - SAP SE\\Documents\\Drexel\\MATH 318\\Week 1\\hw1.csv")
```

**2. Load the data sets into R as a data frame**

```{r}
library(tidyverse)
hw1.df = as_tibble(hw1.csv) # casts to tibble type
print(hw1.df)
```

**3. What are the names of variables? How many samples are there in this dataset?**

-   Variable names: Site, Value.

-   Number of samples: 100

**4. Find the 80% percentile value for each of the variables in the data set.**

```{r}
quantile(hw1.df$Site, .8) # get the 80% percentile value of 'Site'
```

This indicates 7.7534 is higher than 80% of other values of Site.

```{r}
quantile(hw1.df$Value, .8) # get the 80% percentile value of 'Value'
```

This indicates -4.487722 is higher than 80% of other values of 'Value'

**5. Using ggplot2 with this data frame, plot a histogram of each of the variables, using different themes for each of the plots.**

```{r}
library(ggplot2)
```

```{r}
ggplot(data = hw1.df, mapping = aes(x = Site)) + geom_histogram(binwidth = .1, fill = "darkorange") + theme_bw()
```

```{r}
ggplot(data = hw1.df, mapping = aes(x = Value)) + geom_histogram(binwidth = .2, fill = "white") + theme_dark()
```

**6. Plot the data set as a scatter plot (using geom_point) with filled red pluses as the markers.**

```{r}
ggplot(data = hw1.df) + geom_point(mapping = aes(x = Site, y = Value), shape = 3, color="red") + theme_grey()
```

Data follow a linear trend line which shows Value value is increasing at a steady rate as Site value increases.
